DATA 624 Project 1 Part B - Power

### 2020-03-21 DATA624/Project 1-B Power.Rmd
More work on Project 1-B

```{r}
kwh <- read_excel("ResidentialCustomerForecastLoad-624.xlsx") %>%
  select(KWH) %>%
  ts(start = decimal_date(date("1998-01-01")), frequency = 12)

@@

@@

@@

@@

@@

hw_error <- tsCV(kwh, hw, h = h)
adj_hw_error <- tsCV(kwh, hw, h = h, lambda = lambda)
damped_adj_hw_error <- tsCV(kwh, hw, h = h, lambda = lambda, damped = TRUE)
arima_errors <- tsCV(kwh, forecast(auto.arima(kwh), h=h), h = h)

@@

>>>>

```{r}
raw_data <- read_excel("ResidentialCustomerForecastLoad-624.xlsx")
kwh <- raw_data %>%
  select(KWH) %>%
  ts(start = decimal_date(date("1998-01-01")), frequency = 12)

@@

There are some spikes in the ACF that indicate this is not the best model.

@@

This is a bit better than the previous model but there are still ACF spikes outside of the bands.

@@

The preformance of this model is about the same as above.

@@

This model seems to be the best.  There is only one ACF spike outside of the threshold and it only by a small amount.  My working theory is this is the model I should use, but I will check this using cross validation.

@@

arima_forecast <- function(x, h){forecast(Arima(x, order = c(3, 0, 1), seasonal = c(2, 1, 0), include.drift = TRUE), h = h)}

hw_error <- tsCV(kwh, hw, h = h)
adj_hw_error <- tsCV(kwh, hw, h = h, lambda = lambda)
damped_adj_hw_error <- tsCV(kwh, hw, h = h, lambda = lambda, damped = TRUE)
arima_errors <- tsCV(kwh, arima_forecast, h = h)

@@

The ARIMA model had the best cross validation results.

## Model Selection

Given that the ARIMA model minimized the RMSE in the cross validation, I will use it to forecast residential power consumption.

## Forecast

Here's my forcast for the next `r h` months of power usage:

```{r}
my_forecast <- forecast(arima_fit, h = h)
autoplot(my_forecast)
  ggtitle("Forecasted Residential Power Consumption (KWH)") +
  theme(axis.title = element_blank())

my_forecast %>% 
  kable() %>% 
  kable_styling()
```

```{r}
data.frame(my_forecast$mean) %>%
  rename(KWH = my_forecast.mean)
```
